---
title: "assign_1_task_2_esm_244"
author: "Satie Airame"
date: "1/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(here)
library(ggfortify)
library (gghighlight)
library(lubridate)
library(plotly)
library(patchwork)
```


```{r}
world_env_vars <- read_csv(here("data", "world_env_vars.csv")) 

world_env_vars_subset <- world_env_vars %>% 
  select(cropland_cover, tree_canopy_cover, rain_mean_annual, temp_max_warmestMonth, temp_min_coldestMonth, cloudiness, elevation, aspect, slope) 

world_env_vars_subset_pca <- world_env_vars_subset %>% 
  drop_na() %>% 
  scale() %>% 
  prcomp()
world_env_vars_subset_pca$rotation
```


```{r}
world_env_vars_subset_complete <- world_env_vars_subset %>%
  drop_na(cropland_cover, tree_canopy_cover, rain_mean_annual, temp_max_warmestMonth, temp_min_coldestMonth, cloudiness, elevation, aspect, slope)

autoplot(world_env_vars_subset_pca,
         data = world_env_vars_subset_complete,
         loadings = TRUE,
         loadings.label = TRUE)
```

The variables that are positively correlated are:
* cropland_cover and elevation
* rain_mean_annual, tree_canopy_cover, cloudiness

The variables that are negatively correlated are:
* temp_min_coldestMonth and cropland_cover
* temp_max_warmestMonth and slope
* rain_mean_annual and cropland cover
* tree_canopy_cover and cropland_cover

The variables that are not correlated are:
* temp_min_coldestMonth and cloudiness
* tree_canopy_cover and temp_max_warmestMonth
* rain_mean_annual and temp_max_warmestMonth








