---
title: "assign_1_esm_244_ satie_airame"
author: "Satie Airame"
date: "1/17/2021"
output: html_document
---

# Amphibian Abundance recorded by the Sierra Lakes Inventory Project

### Amphibian surveys of Sierra Nevada lakes from 1995-2002.

### Reference: Knapp, R.A., C. Pavelka, E.E. Hegeman, and T.C. Smith. 2020. The Sierra Lakes Inventory Project: Non-Native fish and community composition of lakes and ponds in the Sierra Nevada, California ver 2. Environmental Data Initiative. https://doi.org/10.6073/pasta/d835832d7fd00d9e4466e44eea87fab3



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(patchwork)
library(lubridate)
library(readxl)
library(dplyr)
```

### Graph of total mountain yellow legged frog (Rana mucosa) count each year across all water bodies, by life stage excluding "EggMass." 

```{r, echo = FALSE, message = FALSE, warning = FALSE}
sierra_frogs <- read_excel(here("data", "sierra_amphibians.xlsx"))
```


```{r, echo = FALSE, message = FALSE, warning = FALSE}
ramu <- sierra_frogs %>% 
  filter(amphibian_species == "RAMU") %>% 
  filter(amphibian_life_stage %in% c("Adult", "SubAdult", "Tadpole")) %>% 
  mutate(date_new = ymd(survey_date)) %>% 
  mutate(year_new = year(date_new))
```

```{r, echo = FALSE, message = FALSE, warning = FALSE}
ramu_count <- ramu %>% 
  group_by(year_new) %>% 
  summarize(total_frogs = sum(amphibian_number, na.rm = TRUE))

```

```{r, echo = FALSE, message = FALSE, warning = FALSE}
p1 <- ggplot(data = ramu_count, aes(x = year_new, y = total_frogs))+
  geom_col() +
  labs(x = "Year",
       y = "Total Number (Adults, subadults, tadpoles)",
       title = "Number of Rana mucosa in Sierra Nevada Lakes, 1995 - 2002")

p1
```

### Column graph containing counts (over all years) of combined adult and subadult endangered mountain yellow-legged frogs (Rana mucosa) obsered in 5 lakes with the greatest observed counts. Exclude tadpoles. Consider reformatting from a number to a label "Lake 10025", then use fct_roder to cover it to an ordered factor.

```{r}

ramu_2 <- sierra_frogs %>% 
  filter(amphibian_species == "RAMU") %>% 
  filter(amphibian_life_stage %in% c("Adult", "SubAdult")) %>% 
  mutate(date_new = ymd(survey_date)) %>% 
  mutate(year_new = year(date_new)) %>% 
  add_column(lake_id_2 = "Lake ")
# Would like to add "Lake" in front of each lake number

```

```{r}
ramu_2_unite <- ramu_2 %>% 
  unite("lake_id_3", lake_id_2, lake_id, sep = "")
```


```{r}
ramu_2_count <- ramu_2_unite %>% 
  group_by(lake_id_3) %>% 
  summarize(total_frogs_2 = sum(amphibian_number, na.rm = TRUE))
ramu_2_count
```

```{r}
ramu_2_count_top_5 <- ramu_2_count %>% 
  top_n(5) 
ramu_2_count_top_5

# Need to sort in descending order
```


```{r}
p2 <- ggplot(data = ramu_2_count_top_5, aes(x = lake_id_3, y = total_frogs_2))+
  geom_col() +
  labs(x = NULL,
       y = "Total Number (Adults and Subadults)",
       title = "Number of adult and subadult Rana mucosa at top 5 Sierra lakes")
p2
```

```

### Combine graphs into a single compound figure using the {patchwork} package. Add figure caption.

```{r}
p3 <- p1 + p2 + plot_layout(ncol=1,heights=c(2,1))
p3
```

